{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-11 Paper/main.tex
Miniature Change

		 We created two different error-terms by generating an i.i.d. standard normal error term 	$Z \sim \mathcal{N}(0,1)$ and multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.9} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.6} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}

>>>>

		 We created two different error-terms by generating i.i.d. standard normal errors  $Z \sim \mathcal{N}(0,1)$ and multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios of the responses to test the methods with low and high amounts of noise in the responses. They are created such that the squared multiple correlation coefficient $R^2 = var(\langle X, f\rangle) / (var(\langle X, f\rangle) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.	
		\begin{equation}
			\begin{split}
				Y_{1,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.9} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack \\
				Y_{2,f} & = \langle NIR_{sim}, f\rangle + Z  \biggl\lbrack\frac{var(\langle NIR_{orig}, f\rangle)}{0.6} - var(\langle NIR_{orig}, f\rangle)\biggr\rbrack
			\end{split}
		\end{equation}
